---
title: "Radical framing effects in the ultimatum game (Experimental Results, Discussion, and Supplementary Materials)"
author: "Aaron D. Lightner, Pat Barclay, Edward H. Hagen"
csl: vancouver.csl
output:
  html_document: default
  word_document: default
bibliography: RSOS_pt2_refs.bib
---

## Results

```{r echo=FALSE, warning=FALSE, results='hide', message=FALSE}
library(devtools)
library(tidyverse)
library(car)
library(effsize)
library(lawstat)
library(readr)
library(knitr)
library(reshape2)
library(ggmosaic)
library(effects)
library(gamlss.mx)
library(arm)
library(reshape2)
library(Rmixmod)
library(multcomp)
library(binomTools)
library(gridExtra)
library(broom)
library(AICcmodavg)
library(diagram)
library(visreg)
library(viridis)
install_github('alightner/framingdata2017')
library(framingdata2017)
install_github('alightner/dataAMT2017')
library(dataAMT2017)
#load("~/Desktop/Docs/RSOS data AMT/dataAMT2017/data/UG.data.rda")
df <- dataAMT2017::UG.data
df$offer[df$condition=='control' | df$condition=='windfall'] <- 
  df$offer[df$condition=='control' | df$condition=='windfall'] * 100

df$condition <- factor(df$condition, levels=c('banker', 'control', 
                                              'windfall', 'customer'))

#load("~/Desktop/Docs/RSOS data AMT/dataAMT2017/data/UG.preatt.rda")
#load("~/Desktop/Docs/RSOS data AMT/dataAMT2017/data/UG.presurv.rda")

dfpa <- dataAMT2017::UG.preatt
dfps <- dataAMT2017::UG.presurv
dfps$offer[dfps$condition=='control' | dfps$condition=='windfall'] <- 
  dfps$offer[dfps$condition=='control' | dfps$condition=='windfall'] * 100

dfps$condition <- factor(dfps$condition, levels=c('banker', 'control', 
                                              'windfall', 'customer'))



## p value reporting function
p.function <- function(p) {
  if (p >= 0.001) {
    paste(c("p =", signif(p,3)), collapse = " ")
  } else {
    c("p < 0.001")
  }
}


```

Following our *a priori* criteria, and before analyzing the experimental results, participants were excluded if they did not complete the survey, which was determined by a failure to correctly enter a unique validation code at the end of the survey. This was only attainable if a participant correctly answered two attention check questions during the task. These exclusionary criteria were set out to remove participants less likely to be attentive from analyses. In addition, many other participants left the study beforehand (e.g., while the game was loading or after viewing the consent form - see Figure 5 for attrition data). There did not appear to be a marked change in offer trends between the excluded participants who played the UG (but did not complete the survey) and the analyzed participants who completed the entire study (Figure 6). We refer to the condition with proposers in the banker role as the “banker condition”, and the condition with proposers in the customer role as the “customer condition”.


```{r echo=FALSE, warning=FALSE}
#sd(df$offer[df$condition=='control'])
#sd(df$offer[df$condition=='windfall'])
a <- c(df$offer[df$condition=='control' & df$playerid==1], df$offer[df$condition=='windfall' & df$playerid==1])
b <- c(rep(1, length(df$offer[df$condition=='control' & df$playerid==1])), 
       rep(2, length(df$offer[df$condition=='windfall' & df$playerid==1])))
lv <- leveneTest(a,b)
lvF <- lv$`F value`[1]
lvP <- lv$`Pr(>F)`[1]
flig <- fligner.test(a,b)

shap1 <- shapiro.test(df$offer[df$condition=='banker' & df$playerid==1])
shap2 <- shapiro.test(df$offer[df$condition=='customer' & df$playerid==1])
shap3 <- shapiro.test(df$offer[df$condition=='windfall' & df$playerid==1])
shap4 <- shapiro.test(df$offer[df$condition=='control' & df$playerid==1])

k <- kruskal.test(df$offer[ df$playerid==1] ~ df$condition[ df$playerid==1])

a1 <- wilcox.test(df$offer[df$condition=='control' & df$playerid==1], df$offer[df$condition=='banker' & df$playerid==1])
a2 <- wilcox.test(df$offer[df$condition=='control' & df$playerid==1], df$offer[df$condition=='customer' & df$playerid==1])

m <- lm(offer ~ condition, data=subset(df, playerid==1))
ao <- Anova(m)
aoF <- ao$`F value`[1]
aoP <- ao$`Pr(>F)`[1]

t1 <- t.test(df$offer[df$condition=='control'], 
             df$offer[df$condition=='banker'])
t2 <- t.test(df$offer[df$condition=='control'], 
             df$offer[df$condition=='customer'])


akg1 <- c(df$offer[df$condition=='control' & df$playerid==1],
       df$offer[df$condition=='banker' & df$playerid==1])
akg2 <- c(df$offer[df$condition=='control' & df$playerid==1],
        df$offer[df$condition=='customer' & df$playerid==1])
groups_1 <- as.factor(c(rep(1, length(df$offer[df$condition=='control' & 
                                                df$playerid==1])), 
                       rep(2, length(df$offer[df$condition=='banker' & 
                                                df$playerid==1]))))
groups_2 <- as.factor(c(rep(1, length(df$offer[df$condition=='control' & 
                                                df$playerid==1])), 
                       rep(2, length(df$offer[df$condition=='customer' & 
                                                df$playerid==1]))))
cliff.bank <- cliff.delta(akg1, groups_1)
cliff.cust <- cliff.delta(akg2, groups_2)
cohen.bank <- cohen.d(akg1, groups_1)
cohen.cust <- cohen.d(akg2, groups_2)
```

```{r,echo=FALSE, fig.width=7, fig.height=5, fig.show='hold',fig.align='center'}

phases <- c("Viewed consent form", "Played UG", "Started survey", "Completed survey\nand attention checks")
dff <- data.frame("Studyphase" = factor(phases, levels = phases), "Number" = c(1040, 770, 552, 472))
ggplot(dff, aes(x=Studyphase, y=Number)) + geom_bar(stat='identity') +
     geom_text(aes(x=Studyphase, label=Number), size=3.25, vjust=-1) +
     labs(x='Study phase') + coord_cartesian(ylim=c(0,1250))

```

**Figure 5.** Bar chart representing number of participants during each study phase. Individuals who completed the survey and attention checks were included in our sample (N=472) for analysis.


```{r echo=FALSE, warning=FALSE, fig.align='center', fig.width=10}
mps <- df$userid

p1 <- ggplot(data=subset(dfps, playerid==1 & !(is.na(offer)) & !(userid %in% mps)), aes(x=offer)) + geom_histogram(binwidth = 5) +
  facet_wrap(~condition, ncol=4) + coord_cartesian(ylim=c(0,55)) + labs(x='')

p2 <- ggplot(data=subset(df, playerid==1), aes(x=offer)) + geom_histogram(binwidth = 5) +
  facet_wrap(~condition, ncol=4) + coord_cartesian(ylim=c(0,55)) + labs(x='Offer (%)')

grid.arrange(p1,p2)
```

**Figure 6.** Histogram of proposers' offers by condition, with offers of excluded participants on the top row and offers of included participants on the bottom row.


The biggest differences between offers from excluded vs. included participants were in the windfall condition, where almost all excluded participants offered 0% but almost all included participants offered 50%, and in the control condition, where more excluded participants offered 0% than 50% but almost all included participants offered 50%. Other interesting differences included that in the banker condition, a greater fraction of offers from excluded participants were either 0% or 100% compared to offers from included participants, and that in the customer condition a greater fraction of offers from excluded participants were either 0% or 50% compared to included participants. Henceforth, unless explicitly noted, all analyses will be of data from included participants only.

In our experiment, the central tendency differences between treatment and control conditions were significant and conformed to our predictions, with offers in the banker condition (mean = `r signif(mean(df$offer[df$condition=='banker']),3)`, SD = `r signif(sd(df$offer[df$condition=='banker']),3)`) significantly higher than the control condition (mean = `r signif(mean(df$offer[df$condition=='control']),3)`, SD = `r signif(sd(df$offer[df$condition=='control']),3)`, t = `r signif(t1$statistic,3)`, `r p.function(t1$p.value)`, Cohen's d = `r signif(cohen.bank$estimate,3)`) and offers in the customer condition (mean = `r signif(mean(df$offer[df$condition=='customer']),3)`, SD = `r signif(sd(df$offer[df$condition=='customer']),3)`) significantly lower than the control condition (t = `r signif(t2$statistic,3)`, `r p.function(t2$p.value)`, Cohen's d = `r signif(cohen.cust$estimate,3)`). See Table 2 and Figure 7.

```{r echo=FALSE, warning=FALSE}
dt <- df
dt$offer <- dt$offer/100
dt$condition <- factor(dt$condition, levels=c('control', 'banker', 
                                                 'windfall', 'customer'))
m <- glm(offer ~ condition, family=binomial, subset(dt, playerid==1))
x <- tidy(m)
kable(x, digits = 3, caption = 'Table 2. Logistic regression of mean offers by condition.')
```


```{r echo=FALSE, warning=FALSE}
dt <- df
dt$offer <- dt$offer/100
dt$condition <- factor(dt$condition, levels=c('banker', 'control', 
                                                 'windfall', 'customer'))
m <- glm(offer ~ condition, family=binomial, subset(dt, playerid==1))
plot(allEffects(m), main='')
```

**Figure 7.** Generalized linear model of the mean offer (as a proportion of the maximum possible offer) by condition. Bars indicate +/- 2 SE. See text for details.


The data in each condition were not normally distributed (Shipiro Wilk: banker W = `r signif(shap1$statistic, 3)`, `r p.function(shap1$p.value)`; customer W = `r signif(shap2$statistic, 3)`, `r p.function(shap2$p.value)`; windfall W = `r signif(shap3$statistic, 3)`, `r p.function(shap3$p.value)`; control W = `r signif(shap4$statistic, 3)`, `r p.function(shap4$p.value)`). As stipulated in our *a priori* statistical analyses section we therefore also tested for differences in offers using a non-parametric Kruskal-Wallis rank sum test  ($\chi^2$ = `r signif(k$statistic, 3)`, `r p.function(k$p.value)`). Likewise, pairwise median differences between banker and control conditions (banker median = `r signif(median(df$offer[df$condition=='banker']),3)`, control median = `r signif(median(df$offer[df$condition=='control']),3)`) and customer and control conditions (customer median = `r signif(median(df$offer[df$condition=='customer']),3)`) were re-tested to confirm that our predictions were supported for both banker and customer conditions (banker-control Mann-Whitney U = `r signif(a1$statistic,3)`, `r p.function(a1$p.value)`, and Cliff's Delta = `r signif(cliff.bank$estimate,3)`; customer-control U = `r signif(a2$statistic,3)`, `r p.function(a2$p.value)`, and Cliff's Delta = `r signif(cliff.cust$estimate,3)`).

```{r echo=FALSE, warning=FALSE}
ar1 <- (mean(df$accept[df$playerid==1 & df$condition=='control']))*100
ar2 <- (mean(df$accept[df$playerid==1 & df$condition=='windfall']))*100
fc1 <- (length(df$offer[df$playerid==1 & df$condition=='control' & 
                  df$offer==50])/
  length(df$offer[df$playerid==1 & df$condition=='control']))*100
fc2 <- (length(df$offer[df$playerid==1 & df$condition=='windfall' & 
                  df$offer==50])/
  length(df$offer[df$playerid==1 & df$condition=='windfall']))*100

m <- glm(accept ~ condition*offer, family=binomial, subset(df, playerid==2))
rsq <- Rsq(m)
```

While the offer variance in the windfall vignette condition was lower than that of the control condition (windfall mean = `r signif(mean(df$offer[df$condition=='windfall']),3)`, SD = `r signif(sd(df$offer[df$condition=='windfall']),3)`, IQR = `r signif(IQR(df$offer[df$condition=='windfall']),3)`; control IQR = `r signif(IQR(df$offer[df$condition=='control']),3)`), this difference was not significant (F = `r signif(lvF, 3)`, `r p.function(lvP)`; $\chi^2$ = `r signif(flig$statistic,3)`, `r p.function(flig$p.value)`) using either equality of variances test (i.e., Brown-Forsythe Levene-type and Fligner-Killeen tests), contrary to predictions. It is worth noting, however, that the portion of "fair splits" (i.e., 50-50 offers) among proposers was `r signif(fc1, 3)`% with an acceptance rate of `r signif(ar1, 3)`% in the control condition, and `r signif(fc2, 3)`% fair splits with an acceptance rate of `r signif(ar2, 3)`% in the windfall condition. 

```{r echo=FALSE, warning=FALSE}
over90 <- (length(df$offer[df$offer >= 90 & df$condition=='banker' & df$playerid==1])/length(df$offer[df$condition=='banker' & df$playerid==1]))*100  ## 64.9%

hypoacc <- (length(df$accept[df$accept==1 & df$condition=='customer' & df$playerid==2 & df$offer < 50])/length(df$accept[df$condition=='customer' & df$playerid==2 & df$offer < 50]))*100  ## 68.6%

bankrej <- (length(df$accept[df$accept==0 & df$condition=='banker' & df$playerid==2 & df$offer > 50])/length(df$accept[df$condition=='banker' & df$playerid==2 & df$offer > 50]))*100  ## 20.4%
```

The probability of offer acceptance was modeled using a logistic regression (Table 3 and Figure 8). The probability of offer acceptance was low for small offers, and increased sharply in the control and windfall conditions as a function of offer amount. The customer and banker conditions had "flatter" acceptance probabilities across offer amounts. Tjur's coefficient of discrimination, a measure of fit, was D = `r signif(rsq$D, 3)`. Inspection of the distribution of probabilities for true rejections (Figure 9, top) and true acceptances (Figure 9, bottom) indicated that our model was reasonably good at predicting acceptances but poor at predicting rejections. Overall, the responders' acceptance criteria aligned with our predictions: in the control and windfall conditions, responders largely accepted fair 50-50 splits with some tolerance for "hypo-fair" (i.e., < 50%) offers, but most of the latter were rejected. In the banker condition, `r signif(over90, 3)`% of participants offered 90% or more of their allocation, with modes at 90% (n = 13) and 95% (n = 12). When bankers were responders (in the customer condition), `r signif(hypoacc, 3)`% accepted hypo-fair offers (those < 50%). Customers in the responder role, on the other hand (in the banker condition), rejected `r signif(bankrej, 3)`% of hyper-fair offers (those > 50%). In the customer condition, most of the acceptances (and rejections) were hypo-fair, while most acceptances *and rejections* in the banker condition were "hyper-fair" (i.e., > 50%) offers (Figure 10). 


```{r echo=FALSE, warning=FALSE, message=FALSE}
df$condition <- factor(df$condition, levels=c('control', 'banker', 
                                                 'windfall', 'customer'))
m <- glm(accept~offer*condition, family=binomial, data=subset(df, playerid==2))
x <- tidy(m)
kable(x, digits = 3, caption = 'Table 3. Logistic regression of responder acceptance probability as a function of offer amount by condition. Coefficients are log odds.')
```


```{r echo=FALSE, warning=FALSE, message=FALSE}
visreg(m, xvar='offer', by='condition', scale='response', jitter = TRUE)
```

**Figure 8.** Plot of logistic regression of responders' acceptance probability as a function of offer amount by condition (gray shaded areas indicate 2 SE, rug indicates offers). 


```{r echo=FALSE, warning=FALSE}
d2 <- data.frame(piHat=rsq$piHat, y=rsq$Y)
ggplot(d2, aes(x=piHat)) + geom_histogram(binwidth = 0.025) + facet_wrap(~y, ncol=1) + coord_cartesian(xlim=c(0,1)) +
  labs(x='Probability(1)')
```

**Figure 9.** Plot of fitted probabilities of acceptance in the logistic model that includes experimental condition and offer amount (Figure 8), for true rejections (top) and true acceptances (bottom). If the logistic model has perfect predictability, then true rejections should cluster at 0 and true acceptances should cluster at 1. This logistic model was better at predicting true acceptances (bottom) than true rejections (top). The coefficient of discrimination (Tjur's D) is the difference in the mean probabilities of true acceptances minus the mean probabilities of true rejections. This measure can be used as a logistic regression analogue to an $R^2$ coefficient of determination [@tjur2009].


```{r echo=FALSE, warning=FALSE}
df$fairness <- ifelse(df$offer < 50, 'Hypo', 'Fair')
df$fairness[df$offer > 50] <- 'Hyper'
df$fairness <- factor(df$fairness, levels = c('Hypo', 'Fair', 'Hyper'))
#ggplot(d, aes(offer)) + geom_histogram() + facet_grid(accept ~ condition)

#plot(xtabs(~ accept + condition + fairness, data=df), main='')
ggplot(data=subset(df, playerid==2)) + 
  geom_mosaic(aes(x=product(accept,condition), fill=factor(fairness))) + 
  theme(axis.text.x=element_text(angle=-30, hjust= .1)) + 
  #facet_grid(accept~.) +
  facet_grid(~condition) +
  guides(fill=guide_legend(title = "Fairness", reverse = TRUE)) +
  theme(axis.text.x=element_blank(),axis.ticks.x=element_blank()) +
  labs(x="Condition", 
       y="Reject                                        Accept")
```

**Figure 10.** Mosaic plot of frequencies of responders' acceptance and rejection of offers under 50% ("Hypo"), at 50% ("Fair"), and over 50% ("Hyper") by condition.

```{r echo=FALSE, warning=FALSE, results='hide', message=FALSE}
#load("~/Desktop/Docs/MA Thesis/framingdata2017/data/dataAMT_pilot.rda")

du <- framingdata2017::dataAMT_pilot

a <- du$offer[du$app=='control'& du$playerid==1]
b <- df$offer[df$condition=='control' & df$playerid==1]
pexpconmean <- wilcox.test(a,b)
a <- c(du$offer[du$app=='control'& du$playerid==1], df$offer[df$condition=='control' & df$playerid==1])
b <- factor(c(rep(1, length(du$offer[du$app=='control'& du$playerid==1])), 
              rep(2, length(df$offer[df$condition=='control' & df$playerid==1]))))
c <- leveneTest(a,b)
pexpconsdF <- c$`F value`[1]
pexpconsdP <- c$`Pr(>F)`[1]
###
a <- du$offer[du$app=='customer'& du$playerid==1]
b <- df$offer[df$condition=='customer' & df$playerid==1]
pexpcustmean <- wilcox.test(a,b)
a <- c(du$offer[du$app=='customer'& du$playerid==1], df$offer[df$condition=='customer' & df$playerid==1])
b <- factor(c(rep(1, length(du$offer[du$app=='customer'& du$playerid==1])), 
       rep(2, length(df$offer[df$condition=='customer' & df$playerid==1]))))
c <- leveneTest(a,b)
pexpcustsdF <- c$`F value`[1]
pexpcustsdP <- c$`Pr(>F)`[1]
###
a <- du$offer[du$app=='banker'& du$playerid==1]
b <- df$offer[df$condition=='banker' & df$playerid==1]
pexpbankmean <- wilcox.test(a,b)
a <- c(du$offer[du$app=='banker'& du$playerid==1], df$offer[df$condition=='banker' & df$playerid==1])
b <- factor(c(rep(1, length(du$offer[du$app=='banker'& du$playerid==1])), 
              rep(2, length(df$offer[df$condition=='banker' & df$playerid==1]))))
c <- leveneTest(a,b)
pexpbanksdF <- c$`F value`[1]
pexpbanksdP <- c$`Pr(>F)`[1]

```

The proposers' low offer amounts in the customer condition and high offer amounts in the banker condition appeared to be fairly consistent overall with their reported fair currency fees. In particular, most proposers in the customer condition both reported that a fair currency fee was a low percentage amount and offered low percentage amounts to the bankers. In the banker condition, most proposers both reported that a fair currency fee was a low percentage amount and offered high percentage amounts to the customers (i.e., kept a small bank fee - see Figure 11). 

```{r echo=FALSE, warning=FALSE, results='hide', message=FALSE}
df$offer2 <- df$offer/100
df$currencyfee <- df$currencyfee/100
df$currencyfee[df$condition=='banker'] <- 1 - df$currencyfee[df$condition=='banker']

ggplot(subset(df, playerid==1 & (condition=='banker'| condition=='customer')), aes(x=currencyfee, y=offer2, colour=condition)) + 
  geom_point(alpha=0.75) + #geom_jitter(height=0.025) + 
  geom_abline(linetype='dashed') + 
  scale_colour_viridis(end =0.5, discrete = TRUE) +
  labs(x='Reported fair currency fee', y='Actual offer')


```

**Figure 11.** Amount offered (%) among proposers in the banker and customer conditions, as a function of their reported opinions about fair currency fee (%). Conditions are separately represented by color.


The pilot study results (previously discussed) informed our experimental design and caused us to slightly adjust our initial predictions. To explore the effects of changing our protocol between pilot and experiment, we compare and contrast the results of this experiment to those of the pilot. As discussed in both this section and the "Pilot Study" section, we confirmed our predictions with large effect sizes between control and treatment conditions in both the pilot and the experiment. The offers in both (pilot and experiment) control conditions and both customer conditions did not significantly differ in central tendency (control condition: Mann-Whitney U = `r signif(pexpconmean$statistic,3)`, `r p.function(pexpconmean$p.value)`; customer condition: U = `r signif(pexpcustmean$statistic,3)`, `r p.function(pexpcustmean$p.value)`) or variance (control: Brown-Forsythe Levene F = `r signif(pexpconsdF,3)`, `r p.function(pexpconsdP)`; customer: F = `r signif(pexpcustsdF,3)`, `r p.function(pexpcustsdP)`). The banker condition in the experiment, however, yielded higher offers (U = `r signif(pexpbankmean$statistic,3)`, `r p.function(pexpbankmean$p.value)`) with lower offer variance (F = `r signif(pexpbanksdF,3)`, `r p.function(pexpbanksdP)`) than the banker condition in our pilot. The latter had a significantly higher variance than the other conditions in the study, which as discussed, was likely an artifact of confusing instructions (see Pilot Study). These comparisons indicate that the minor adjustments we made to study instructions following the pilot study improved our results. See Figure 12.

```{r echo=FALSE, warning=FALSE}
p1 <- ggplot(data=subset(du, playerid==1), aes(x=offer)) + geom_histogram(binwidth = 5) +
  facet_wrap(~app) + labs(x='')
p2 <- ggplot(data=subset(df, playerid==1 & condition != 'windfall'), aes(x=offer)) + geom_histogram(binwidth = 5) +
  facet_wrap(~condition) + labs(x='Offer (%)')
grid.arrange(p1,p2)
```

**Figure 12.** Histogram of proposers' offers by condition, with pilot data (top row) and experimental data (bottom row). Study instructions were tweaked following the pilot study. The windfall condition is omitted in this figure because it did not have a corresponding pilot condition.


## Discussion

```{r echo=FALSE, warning=FALSE, results='hide', message=FALSE}

d.vals <- c(0.33, 0.29, 0.27, 0.49, 0.56,0.46,0.47,0.6,0.35,0.57,
            0.5,0.5888977,
            0.6411336,1.09095,2.035155)
d.inf <- c(0.08, -0.02,0.08,0.18,0.14,0.06,-0.1,0.02,0.01,0.09,
           0.01,-0.02540322,
           0.04482694,0.6857637,1.571529)
d.sup <- c(0.58,0.59,0.45,0.8,0.99,0.86,1.05,1.18, 0.69,1.06,0.98,
           1.20319868,1.23744036,1.4961360,2.4987)
frames <- c('Teamwork\n(Spontaneous)','Teamwork vs. Taxes\n(Labeled)',
            'Teamwork vs. No-teamwork\n(Comprehensive)',
            'Community vs. Wall Street', 'Giving vs. Taking',
            'Osotua (Kenya, all)', 'Osotua (Kenya, player 1)',
            'Osotua (Kenya, player 2)', 'Osotua (U.S., all)', 
            'Osotua (U.S., player 1)', 'Osotua (U.S., player 2)',
            'Sovkhoz','Obschina','**Customer','**Banker')
frames <- factor(frames, levels= sort(frames, decreasing = TRUE))
Games <- c(rep('Public Goods',4),'Dictator',rep('Trust',6),rep('Public Goods',2), rep('Ultimatum',2))
d.table <- data.frame(d.vals,d.inf,d.sup,frames,Games)
d.table <- arrange(d.table, d.vals)

ggplot(d.table, aes(x=frames,y=d.vals)) +
  geom_point(aes(colour=Games)) +
  #geom_bar(aes(fill=games),position=position_dodge(0.9),stat="identity") +
  # geom_hline(yintercept = 0.2, linetype=3) +
  #geom_hline(yintercept = 0.5, linetype=3) +
 # geom_hline(yintercept = 0.8, linetype=3) +
  geom_errorbar(aes(ymin=d.inf, ymax=d.sup), width=.2,
                position=position_dodge(.9)) + 
  coord_flip() + labs(x='Frames', y='Effect size (|d|)')

## Note: see effect_size_figure_framing.R script in this folder to see computations
```

**Figure 13.** Effect sizes (absolute values of Cohen's d) from this study (denoted by "**") and a representative sample of previous framing studies. Colors represent game type and bars indicate 95% CI. For reference, d = 0.8 is considered a large by convention.



```{r echo=FALSE, warning=FALSE, results='hide', message=FALSE}
dfps$condition <- factor(dfps$condition, levels=c('control', 'banker',
                                                  'windfall', 'customer'))
dfps$excluded <- factor(!(dfps$userid %in% df$userid))
dfps$offer2 <- dfps$offer/100
omitperc <- (1 - ((dim(df)[1])/(dim(subset(dfps, !is.na(offer2)))[1])))*100
```

## Supplementary materials (experimental study)

```{r echo=FALSE, warning=FALSE, results='hide', message=FALSE}
m <- glm(offer2 ~ condition*excluded, family=binomial, data=dfps)
m1 <- Anova(m, 3)
m1p <- (m1$`Pr(>Chisq)`)[3]

in50 <- length(df$offer[df$playerid==1 & df$offer==50 & (df$condition=='control' | df$condition=='windfall')])/length(df$offer[df$playerid==1 & (df$condition=='control' | df$condition=='windfall')])  ## 79.1%

in0 <- length(df$offer[df$playerid==1 & df$offer==0 & (df$condition=='control' | df$condition=='windfall')])/length(df$offer[df$playerid==1 & (df$condition=='control' | df$condition=='windfall')])  ## 7.0%

out50 <- length(na.omit(dfps$offer[dfps$playerid==1 & dfps$excluded==TRUE & dfps$offer==50 & (dfps$condition=='control' | dfps$condition=='windfall')]))/length(na.omit(dfps$offer[dfps$playerid==1 & dfps$excluded==TRUE & (dfps$condition=='control' | dfps$condition=='windfall')]))  ## 21.4%

out0 <- length(na.omit(dfps$offer[dfps$playerid==1 & dfps$excluded==TRUE & dfps$offer==0 & (dfps$condition=='control' | dfps$condition=='windfall')]))/length(na.omit(dfps$offer[dfps$playerid==1 & dfps$excluded==TRUE & (dfps$condition=='control' | dfps$condition=='windfall')]))  ## 60%


quit <- subset(dfps, !(userid %in% dfpa$userid) & 
                 excluded==TRUE & 
                 (condition=='control' | condition=='windfall'))
quitrej <- (1 - sum(quit$accept, na.rm=TRUE)/length(na.omit(quit$accept)))*100
quitoffer <- mean(quit$offer, na.rm=TRUE)
```

Using our *a priori* exclusion criteria, we omitted data from `r signif(omitperc,3)`% of participants who made an offer in the UG. It is therefore important to assess how the excluded offers differed from the included offers. Figure 6 depicts the distributions of excluded offers in each condition vs. included offers. By visual inspection, the distributions of offers in the banker (left) and customer (right) conditions were fairly similar in excluded (top) and included (bottom) participants. The distributions in the control and windfall conditions, however, were quite different. Included participants almost always offered 50% in both of these conditions, whereas excluded participants often offered 0% (specifically, in these two conditions, `r signif(in50,3)`% of the included participants offered 50% and only `r signif(in0,3)`% offered 0%; in contrast, `r signif(out50,3)`% of excluded participants offered 50% and `r signif(out0,3)`% offered 0%). These differences had only a marginal impact on our main results. We fitted a model of offers by condition that included all participants (N = 770 instead of N = 472). Results were nearly identical to those depicted in Table 2 and Figure 7. We also fitted a model with an additional variable that indicated excluded status. The main effect of condition was still highly significant, there was no significant main effect of exclusion on offers, and there was only a marginally significant exclusion X condition interaction (`r p.function(m1p)`). We do not have a good explanation for the propensity of excluded participants to offer 0% in the control and windfall conditions. Many control and windfall participants who opted out immediately after the game/before the survey had low offers and high rejection rates (`r signif(quitrej,3)`% rejected, mean = `r signif(quitoffer,3)`%), and most others were excluded for their failure to pass attention checks. 

```{r echo=FALSE, warning=FALSE, results='hide', message=FALSE}
plot(allEffects(m), main='', ylab='offer')
#Anova(m, 3)
#summary(m)
```

**Figure S1.** Generalized linear model of offers by condition and included vs. excluded status. Error bars indicate +/- 2 SE.


```{r echo=FALSE, warning=FALSE}
#m1 <- Anova(m, 3)
x <- tidy(m1)
kable(x, digits = 3, caption = 'Table S1. ANOVA results for condition X excluded results.')
```


```{r echo=FALSE, warning=FALSE}
x <- tidy(m)
kable(x, digits = 3, caption = 'Table S2. Summary results for condition X excluded results.')
```


```{r echo=FALSE, warning=FALSE, results='hide', message=FALSE}
ggplot(subset(df, (condition=='banker' | condition=='customer') & 
                playerid==2), aes(x=offer)) + 
  geom_histogram() + facet_grid(condition~accept)
```

**Figure S2.** Histograms of offer amounts in the currency exchange treatment conditions by condition and responders' acceptance status (1 = accepted, 0 = rejected). 

```{r echo=FALSE, warning=FALSE, results='hide', message=FALSE}
ggplot(subset(df, (condition=='control' | condition=='windfall') & 
                playerid==2), aes(x=offer)) + 
  geom_histogram() + facet_grid(condition~accept)
```

**Figure S3.** Histograms of offer amounts in the control and windfall conditions by condition and responders' acceptance status (1 = accepted, 0 = rejected). 


## References





